Characteristics of Top Songs Has Changed from Pandemic Brain

### 2024-04-01 paper/paper.qmd
Updated causal model size

# NOTE: Had to save diagram and read it in as a image since grViz can be only render in HTML and 
# not in PDFs 
# Referenced https://stackoverflow.com/questions/23861000/displaying-images-in-r-in-version-3-1-0
the_image <- readPNG("casual_model.png")
plot.new()
rasterImage(the_image, 0, 0, 0.7, 1)
```

>>>>

# NOTE: Had to save diagram and read it in as a image since grViz can be only render in HTML and 
# not in PDFs 
# Referenced https://stackoverflow.com/questions/23861000/displaying-images-in-r-in-version-3-1-0
the_image <- readPNG("casual_model.png")
plot.new()
rasterImage(the_image, 0, 0, 0.9, 1.13)
```
